Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-15 ms.tex
editing intro, adding to intro

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}

@@

\begin{abstract}
We present full-sky maps of dust optical depth and temperature derived from 
the \cite{FDS99} two-component dust emission model fitted to \PLANCK~217, 353, 
545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the optical 
depth and temperature maps have angular resolution of $6.1'$. Such maps serve 
as an important alternative to and comparison for other dust 
emission models, especially the single modified blackbody (MBB) model in which 
$\beta$ and $T$ both vary spatially. We also expect the derived optical 
depth to provide valuable cross-checks for other dust-column related data 
products, specifically the \cite{SFD} map, which assumed 
$\beta = 2$ single-component dust emission and included a temperature map of 
inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
best-fit two-component spectral energy distributions to those of the 
\cite{planckdust} single-component parametrization.
%mention the enhanced temperature resolution relative to SFD
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

\section{Introduction}
%why dust important in astronomy/astrophysics
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. At mid-infrared
and far-infrared wavelengths, Galactic dust emission is a major contributor
to the observed sky intensity. In the optical and ultraviolet, extinction
by foreground dust grains attenuates the signal from extragalactic sources
over the entire sky. Understanding the properties of dust in the interstellar 
medium (ISM) is valuable in its own right, as the ISM is the site of star 
formation, thereby playing a crucial role in galaxy evolution. Equally if not 
more important to the practice of astronomy, however, is accounting for dust 
as a foreground which reddens optical/UV observations and superimposes 
Galactic emission on low-frequency observations of the 
cosmic microwave background (CMB). 
%specify ``low frequency more precisely eventually

@@

%maybe say instead ``over the past 30/40 years...''
%Barnard first recognized evidence for dust in astronomical observations, and
%ever since it has been mapped in increasing detail. 
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. High-latitude complexes of 
resolved infrared sources were first identified by \cite{low84} using 
\IRAS~60$\mu$m and 100$\mu$m observations \citep{wheelock94}. This so-called 
``infrared cirrus,'' attributable to thermal emission from large dust grains in
the interstellar medium, has since been probed in greater detail by a variety 
of instruments and detected over virtually the entire sky. Beginning in 1989, 
DIRBE  mapped the full sky at ten infrared wavelengths from 1.25$\mu$m to 
240$\mu$m with a reliable zero point, but inferior 0.7$^{\circ}$ angular 
resolution \citep{boggess92}.mention FIRAS specifically, since it is important 
to FDS99.

@@

\cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, this model should be useful in constructing predictions of dust
emission over a very broad range of wavelengths. This includes low frequencies,
which \cite{planckdust} admit their model does not adequately fit, and also
data near the peak of the dust SED, for example Akari. We also anticipate 
the optical depth map we derive will be useful as a comparison for extinction
estimates based directly upon optical/NIR observations of stars.

>>>>

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}
\newcommand{\AKARI}{{\it Akari}}

@@

\begin{abstract}
We present full-sky maps of dust optical depth and temperature derived by 
applying the \cite{FDS99} two-component dust emission model fitted to 
\PLANCK~217, 353, 545, 857 GHz and \cite{SFD} \IRAS~100$\mu$m data. Both the 
optical depth and temperature maps have angular resolution of $6.1'$. Such maps
 serve as an important alternative to and comparison for other dust 
emission models, especially the single modified blackbody (MBB) model in which 
$\beta$ and $T$ both vary spatially. We also expect the derived optical 
depth to provide valuable cross-checks for other dust-column related data 
products, specifically the \cite{SFD} map, which assumed 
$\beta = 2$ single-component dust emission and included a temperature map of 
inferior $\sim$$1.3^{\circ}$ resolution. We briefly compare our 
best-fit two-component spectral energy distributions to those of the 
\cite{planckdust} single-component parametrization.
%mention the enhanced temperature resolution relative to SFD
%Our optical depth map will also provide a useful reference for dust maps 
%based on stellar colors rather than infrared emission.
\end{abstract}

\section{Introduction}
%why dust important in astronomy/astrophysics
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. At mid-infrared
and far-infrared wavelengths, Galactic dust emission is a major contributor
to the observed sky intensity. In the optical and ultraviolet, extinction
by foreground dust grains attenuates the signal from extragalactic sources
over the entire sky. Understanding the properties of dust in the interstellar 
medium (ISM) is valuable in its own right, as the ISM is the site of star 
formation, thereby playing a crucial role in galaxy evolution. Equally, or 
perhaps even more important to the practice of astronomy, however, is 
accurately accounting for dust as a foreground which reddens optical/UV o
bservations and superimposes Galactic emission on low-frequency observations 
of the cosmic microwave background (CMB). 
%specify ``low frequency more precisely eventually
% somewhere mention re-radiation

@@

%maybe say instead ``over the past 30/40 years...''
%Barnard first recognized evidence for dust in astronomical observations, and
%ever since it has been mapped in increasing detail. 
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. IRAS, with its $\sim$6$'$ 
resolution, revolutionized the study of Galactic dust emission, first revealing
 the high-latitude ``infrared cirrus'' using \IRAS~60$\mu$m and 100$\mu$m 
observations \citep{low84, wheelock94}. Beginning in 1989, DIRBE  mapped the 
full sky at ten infrared wavelengths from 1.25$\mu$m to 240$\mu$m with a 
reliable zero point, but inferior 0.7$^{\circ}$ angular resolution 
\citep{boggess92}.mention FIRAS specifically, since it is important to FDS99.

@@

With the advent of the Planck mission, we have an important opportunity to
revisit foreground predictions in light of their superb data. Brief Planck
background. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, this model should be useful in constructing predictions of dust
emission over a very broad range of wavelengths. This includes low frequencies,
which \cite{planckdust} admit their model does not adequately fit, and also
data near the peak of the dust SED, for example Akari. We also anticipate 
the optical depth map we derive will be useful as a comparison for extinction
estimates based directly upon optical/NIR observations of stars.
